\documentclass[12pt,a4paper]{report}
\setlength\textwidth{145mm}
\setlength\textheight{247mm}
\setlength\oddsidemargin{15mm}
\setlength\evensidemargin{15mm}
\setlength\topmargin{0mm}
\setlength\headsep{0mm}
\setlength\headheight{0mm}
\usepackage[a-2u]{pdfx}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\let\openright=\clearpage

% Thesis title in English (exactly as in the formal assignment)
\def\ThesisTitle{Measuring the Neutrino Magnetic Moment in the NOvA Near Detector}

% Author of the thesis
\def\ThesisAuthor{Róbert Králik}

% Loaction of the University
\def\DeptLocation{Brighton, United Kingdom}

% Year when the thesis is submitted
\def\MonthAndYearSubmitted{April 2024}

% Name of the University
\def\Department{School of Mathematical and Physical Sciences}
\def\University{University of Sussex}

% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Institute}

% Thesis supervisor: name, surname and titles
\def\Supervisor{Dr~Lily~Asquith}
\def\SecondSupervisor{Prof~Jeffrey~Hartnell}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, a person who lent the software, etc.)
\def\Dedication{%
I want to dedicate this thesis to all the people that supported me through entire past year. They gave me strength and courage to finish this piece of work and to not give up entirely.

This includes my dear dear friend from my home in Poprad, my friend from Prague, especially Raju, Efka, Beka and Tomas, who gave me so much needed comfort when I needed it.

I want to thank all of the people at the LDT, where I write these last words and who has been most helpful during these hard past days. Thanks you that you are!

I also dedicate this thesis to my family, who supports me as much as they can.

Also to my colleagues at the NOvA experiment, who helped me and guided me in my academic path to become a scientist and none of this would have ever happened without a large portion of them, mainly to the conveners of the sterile neutrino group, Gavin Davies, Brian Rebel and Adam Aurisano, and also to Jeremy Hewes and Pavel Snopok. All of which have been a great help for me.

Last but not least I want to dedicate this thesis to my supervisor who introduced me to this wonderful world of neutrinos, where I found many of my passions.  
}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\Abstract{%
%NOvA sterile neutrinos search via neutral current (NC) disappearance analysis is moving to a two-detector fit method to be able to fit to a wider range of sterile neutrino oscillations parameters. This introduces among other things a bigger contribution of the neutrino flux systematic uncertainty, which currently makes up the largest overall uncertainty for the ongoing NC disappearance analysis. This thesis focuses on reducing this uncertainty and looks for different ways of making a more precise prediction of the neutrino flux. We point out Horn-Off analysis as the base for doing so and describe the production of a new Horn-Off simulation and the analysis of the Horn-Off results. We were not able to draw any conclusions that would reduce the NC disappearance systematic uncertainty, but the results showed herein can be helpful in the future attempts at a better neutrino flux prediction and a lower neutrino flux systematic uncertainty.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces
\def\Keywords{%
{neutrino} {neutrinos} {NOvA} {electromagnetic} {calibration}
}

\begin{document}
\openright

\vbox to 0.5\vsize{
\setlength\parindent{0mm}
\setlength\parskip{0mm}

\begin{center}
\Department, \University

DOCTORAL THESIS

\hrulefill

\vspace{5mm}

\begin{large}
\ThesisTitle
\end{large}

\vspace{2mm}

\hrulefill

by \ThesisAuthor

with supervision from \Supervisor\ and secondary supervision from \SecondSupervisor

\vspace{15mm}

\textbf{ABSTRACT}
\end{center}
\Abstract

\vspace{15mm}
Keywords:
\Keywords

\vss}

\newpage
\end{document}
